\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{cite}
\usepackage[most]{tcolorbox}

\title{\textbf{Unlocking the Microscale: How Digital Rock Physics Can Secure Supply Chains for UK and European Critical Minerals}}
\author{Hannah P. Menke \and Maja Rücker}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
The United Kingdom and Europe face acute supply chain vulnerabilities for Critical Raw Materials (CRMs) essential for the energy transition and defense. While policy frameworks such as the UK Critical Minerals Strategy and the EU Critical Raw Materials Act (CRMA) set aggressive targets for domestic extraction, processing, and recycling, the technical means to achieve extreme efficiency from increasingly complex, low-grade ores lag behind. The ``Digital Rocks'' or Digital Rock Physics (DRP) community—historically anchored in the oil and gas sector—possesses deep expertise in multi-scale, multi-modal imaging (including CT, nano-CT, MRI, PET, and FIB-SEM) and pore-scale fluid simulation. This white paper proposes a coordinated pivot of this expertise towards complex ore characterization, specific extraction technologies like Direct Lithium Extraction (DLE), and mine waste valorization. By employing DRP to shorten evaluation times, lower environmental impacts, and design the next generation of synthetic porous materials, the UK and Europe can establish a stronger technological position in the global race for secure, sustainable critical minerals.
\end{abstract}

\section{Context: The Geopolitical Imperative and the Global Race}
The global transition to clean energy technologies has triggered skyrocketing demand for critical minerals such as lithium, cobalt, rare earth elements (REEs), and graphite. For instance, global lithium demand surged by nearly 30\% in 2024 alone \cite{iea_outlook_2025}. Yet, this demand increase coincides with a supply squeeze and an investment paradox: as highlighted by the International Energy Agency's (IEA) Global Critical Minerals Outlook 2025, global mining exploration activity plateaued in 2024 and investment growth slowed markedly \cite{iea_outlook_2025}. Consequently, achieving extreme efficiency and yield optimization from existing deposits is now more critical than ever.

Compounding this issue is the hyper-concentration of the market. The IEA reports that the average market share of the top three refining nations for key energy minerals rose to 86\% in 2024 \cite{iea_outlook_2025}. In response, the EU Critical Raw Materials Act (CRMA) established 2030 benchmarks requiring 10\% extraction, 40\% processing, and 25\% recycling to occur domestically \cite{eu_crma_2024}. Concurrently, the UK's strategy focuses on resilient supply chains, domestic capability, and leveraging world-leading academic strengths \cite{uk_strategy_2022}.

Globally, the United States is also funding advanced mining innovation through programs such as ARPA-E's MINER portfolio and the DOE's \$80M ``Mine of the Future'' Proving Ground Initiative \cite{doe_arpae, doe_mine_future_2025}. The UK and Europe should mobilize their existing DRP communities to maintain transatlantic competitiveness and foster effective collaboration. As ore grades drop globally, the ``easy'' deposits have largely vanished, meaning the new frontier of mining requires far greater micro-scale precision \cite{calvo_copper_2016}.

\section{The Digital Rocks Paradigm}
Digital Rock Physics (DRP) utilizes a comprehensive suite of 3D and 4D imaging technologies to systematically map the structure of any porous material. While often associated primarily with X-ray micro-computed tomography ($\mu$CT), DRP actually spans a much broader array of multi-modal techniques. This includes medical and industrial CT, nano-CT, Positron Emission Tomography (PET), Magnetic Resonance Imaging (MRI), Nuclear Magnetic Resonance (NMR), Focused Ion Beam Scanning Electron Microscopy (FIB-SEM), and Helium Ion Microscopy (HIM). Coupling these diverse imaging methods with advanced image processing, AI-driven segmentation, and numerical simulations creates a unified platform for tracking mass, charge, and fluid flow \cite{drp_blunt_2013}.

Historically, this toolkit was developed to optimize hydrocarbon extraction. However, as the energy transition accelerates, there is a strong case for pivoting this existing infrastructure—including synchrotrons, lab-scale scanners, and supercomputing clusters—towards hard-rock mining and mineralogy. 

Crucially, the UK and Europe already host much of the enabling infrastructure needed for this shift. Diamond Light Source supports tomography and correlative imaging across beamlines including I13, I12, I14, and DIAD; ESRF's BM05 imaging line provides high-energy XCT and phase-contrast imaging for 3D materials characterization; and PSI's TOMCAT platform spans fast micrometer-scale to sub-100-nm tomography for geoscience and energy-materials research \cite{diamond_tomography_2026, esrf_bm05_2026, psi_tomcat_2025}. The strategic challenge is therefore coordination, shared data standards, and translation into mineral-processing workflows rather than building capability from scratch.

\begin{figure}[htbp]
\centering
\small
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{|p{0.225\textwidth}|p{0.225\textwidth}|p{0.225\textwidth}|p{0.225\textwidth}|}
\hline
\parbox[t]{0.215\textwidth}{\textbf{Exploration}\newline 3D texture priors\newline AI training data\newline rapid screening of complex ores} &
\parbox[t]{0.215\textwidth}{\textbf{Characterization}\newline mineral associations\newline liberation metrics\newline correlative chemistry + structure} &
\parbox[t]{0.215\textwidth}{\textbf{Processing \& Extraction}\newline breakage behavior\newline leach-flow pathways\newline porous sorbent design} &
\parbox[t]{0.215\textwidth}{\textbf{Recycling \& Tailings}\newline sensor calibration\newline black-mass texture\newline secondary resource mapping} \\
\hline
\end{tabular}
\caption{Where Digital Rock Physics can add decision-relevant information across the critical-minerals value chain.}
\label{fig:drp_value_chain}
\end{figure}

Taking inspiration from the US DOE National Energy Technology Laboratory’s ``Digital Rocks Portal,'' there is a strong case for establishing a federated European ``Digital Ore Database'' to share multi-modal tomographic data of critical mineral deposits, thereby democratizing access to high-resolution structural data \cite{netl_digitalrocks, digitalrocks_portal_2023}.

\section{Pillar I: Exploration and Advanced Characterization}
The implementation of DRP fundamentally shifts mineral exploration strategies, particularly by fueling AI-based exploration. The IEA explicitly identifies AI-based geological exploration as a promising innovation for the future \cite{iea_outlook_2025, ai_mineral_prospectivity_2011}. DRP provides ultra-high-resolution, 3D ground-truth datasets that can materially improve these predictive geological models. Furthermore, DRP can shorten the timeline from initial discovery to commercial production by enabling faster orebody assessment using advanced sensing and analytical methods \cite{doe_arpae}.

Moving beyond traditional 2D thin sections alone, multi-modal tomographic approaches (ranging from macro-CT down to nano-CT) fully quantify 3D mineral associations, grain sizes, and liberation characteristics. When unified with SEM-EDX-based automated mineralogy via correlative workflows, researchers can locate finely disseminated or texturally complex critical minerals that would otherwise escape detection \cite{buyse_correlative_2023}. These data-rich models also support predictive geometallurgy by integrating sparse process data into spatial orebody models before full-scale mining, improving flowsheet design from the outset \cite{lishchuk_predictive_2019}.

\begin{tcolorbox}[enhanced, colback=blue!3!white, colframe=blue!35!black, title=\textbf{Illustrative Case Study: Correlative Imaging for Complex Pegmatites}, fonttitle=\bfseries, arc=1.5mm, boxrule=0.8pt]
Buyse et al. combined X-ray micro-CT with SEM-EDX automated mineralogy to resolve internal mineral relationships in Sn-Nb-Ta pegmatites and to build a mineral library for 3D interpretation \cite{buyse_correlative_2023}. The direct implication for critical minerals is practical: similar workflows can be adapted to lithium-bearing pegmatites and other texturally complex ores where 2D sections alone are an incomplete guide to processing behavior.
\end{tcolorbox}

\section{Pillar II: Optimizing Mineral Processing and Extraction}
The extraction of critical minerals is notoriously energy- and water-intensive, yet DRP offers robust pathways to optimize these core processes. For example, comminution (crushing and grinding) is an exceptionally energy-intensive step, accounting for vast amounts of global electricity consumption and often exceeding 50\% of a single mine site's power demand \cite{norgate_comminution_2010}. DRP enables microstructurally informed mineral liberation and breakage studies that can support more selective comminution strategies \cite{kyle_processing_2015}. 

Similarly, in operations such as in-situ and heap leaching, engineers can utilize dynamic imaging (e.g., PET or MRI) and simulate pore-scale fluid flow to safely map and understand the transport of lixivium (leaching fluid) \cite{mri_heap_leach_2015}. This deep operational understanding optimizes permeability and dissolution rates for critical minerals, circumventing the need to physically excavate millions of tons of waste rock. Furthermore, DRP is central to characterizing the complex matrices involved in emerging Direct Extraction Technologies. Engineered porous materials such as metal-organic frameworks (MOFs), zeolites, and ion-selective membranes are increasingly being explored for lower-footprint separations, including lithium extraction from brines \cite{mofs_lithium_2026, farber_science_2025}. For lithium-brine systems, the relevant imaging target is often not the brine alone but the pore architecture, accessibility, degradation, and cycling behavior of the sorbents or membranes that control selectivity and throughput.

\section{Pillar III: Tailings Valorization and the Circular Economy}
Developing a circular economy is a cornerstone of both UK and EU critical minerals strategies, particularly regarding the concept of finding treasure in trash. Legacy mine tailings frequently contain significant, unrecovered amounts of critical minerals such as tellurium, antimony, and tungsten. Indeed, the IEA Outlook highlights the ``re-mining of tailings'' as a primary innovation area necessary to bridge looming supply deficits \cite{iea_outlook_2025}, and recent work frames mine-tailings valorization explicitly around recovery of critical materials \cite{araya_tailings_2020}. 

To effectively recycle these materials, advanced sorting mechanisms need to be deployed and precisely calibrated. While the IEA points to advanced sorting technologies for macro-scale recycling \cite{iea_outlook_2025}, high-resolution 3D imaging acts as the fundamental micro-scale calibration tool for these robust industrial sensors. Multi-scale DRP methods can be broadly applied to characterize unconventional secondary feedstocks—like coal refuse, fly ash, and acid mine drainage—across Europe's industrial heartlands. Furthermore, advanced techniques like FIB-SEM and nano-CT can characterize e-waste and complex battery ``black mass'' at sub-micron scales to optimize both mechanical and chemical recycling pathways by mapping structural degradation and elemental composition \cite{battery_blackmass_2021}.

\begin{tcolorbox}[enhanced, colback=green!3!white, colframe=green!35!black, title=\textbf{Illustrative Case Study: Black-Mass Characterization}, fonttitle=\bfseries, arc=1.5mm, boxrule=0.8pt]
Vanderbruggen et al. showed that automated mineralogy can be used to characterize the composition and texture of spent lithium-ion batteries in a way that is directly relevant to recycling process design \cite{battery_blackmass_2021}. For a DRP-led critical-minerals agenda, this is important because it moves ``urban mining'' from bulk assay toward texture-aware process optimization, where liberation, coating residues, and phase associations can all influence recovery.
\end{tcolorbox}

\section{Next-Generation Digital Rocks: Expanding the Horizon}
As the field of Digital Rock Physics matures, it should expand its capabilities to address increasingly complex chemical and synthetic challenges. Foremost among these is the integration of chemistry with structure via correlative microscopy \cite{buyse_correlative_2023}. Digital rocks should evolve beyond purely physical characterization metrics, such as porosity and permeability, to provide explicit chemical context directly to 3D structures. The field should adopt multi-modal correlative workflows that register 2D elemental data from thin sections or SEM-EDX-based automated mineralogy directly onto 3D structural volumes. This chemical painting of 3D structures is important for tracking elemental speciation and reactive transport during complex, multi-phase extraction processes.

The same shift also extends the DRP toolkit from natural geology to engineered materials. Applying these imaging and simulation techniques to synthetic porous media—such as MOFs, zeolites, ion-imprinted membranes, and battery electrodes—has growing relevance for both DLE and downstream clean-energy technologies. Building on recent frameworks established in the literature, DRP techniques can be used to design these porous structures across length scales ranging from angstroms to centimeters, with the aim of regulating the flow of mass, charge, heat, pressure, and radiation \cite{farber_science_2025}. Utilizing tools like NMR to probe sub-nanometer pores alongside macroscopic CT can help optimize surface-area-to-volume efficiency in entirely synthetic domains.

\section{The AI Revolution in Digital Rocks: Surrogates and Upscaling}
The integration of Machine Learning (ML) is fundamentally transforming Digital Rock Physics by directly addressing its historical bottleneck: the extreme computational cost of pore-scale simulations. Traditional DRP simulations—particularly those modeling multi-phase reactive transport—often require prohibitive supercomputing resources. Today, image-based deep-learning surrogates can predict key petrophysical properties directly from microstructural images \cite{graczyk_dl_porosity_2020}. More broadly, physics-informed ML is emerging as a practical route for accelerating complex coupled simulations while retaining physical consistency \cite{karniadakis_piml_2021}.

Furthermore, Physics-Informed Neural Networks (PINNs) can improve the reliability of these models. Unlike standard data-driven AI, PINNs natively embed physical laws (such as Navier-Stokes equations for fluid flow) directly into their loss functions. This mechanism helps ensure that the model predictions remain physically plausible even when tomographic data is sparse or noisy \cite{raissi_pinns_2019}.

Crucially, ML offers one credible route through the DRP ``upscaling'' challenge. Because high-resolution imaging (like nano-CT) is confined to microscopic sample volumes, translating those insights to the macroscopic mine-site scale has always been difficult. Modern ML workflows address this by identifying representative microscopic texture patterns across large datasets, running targeted physics simulations on those key textures, and upscaling the resulting physical properties to the core and reservoir scale \cite{ml_upscaling_drp_2024}. The integration of AI and physics therefore has the potential to extend DRP from a microscopic analytical tool into a macro-scale predictive framework.

\section{Environmental Impact and Sustainability}
The deployment of DRP also carries significant implications for environmental sustainability. Regarding carbon storage (CCUS), leveraging DRP can support safer and faster study of $CO_2$ mineralisation inside mafic and ultramafic rocks. Building on successes like the CarbFix project in Iceland \cite{matter_carbfix_2009}, performing CCUS alongside extraction operations offers a dual benefit: securing domestic resources while contributing to permanent carbon sequestration and improving understanding of dynamic subsurface gas storage \cite{kelemen_peridotite_2020, menke_hydrogen_2024}. Furthermore, fast X-ray imaging improves our understanding of wettability and multiphase flow in porous media, insights that are transferable to flotation and leaching process design \cite{bartels_fast_xray_2017}.

\section{The Road Ahead: Challenges and Recommendations}
To fully realize the potential of DRP in securing critical minerals, several hurdles must be addressed. There is a clear need for standardization, particularly concerning imaging protocols and machine learning models across the European research and industrial community. Additionally, significant technical challenges remain in upscaling, specifically in bridging the wide gap from nano-scale structural data (FIB-SEM/nano-CT) and micro-scale up to the core scale (Macro-CT/MRI/PET), and ultimately mapping that granular data to the massive mine-site scale.

To overcome these challenges, the recommendations below are framed as near-term actions that could be initiated within a single public funding cycle:

\begin{tcolorbox}[enhanced, colback=gray!3!white, colframe=blue!40!black, title=\Large\textbf{Key Policy Recommendations}, colbacktitle=blue!40!black, drop fuzzy shadow, fonttitle=\bfseries, breakable, arc=2mm, boxrule=1pt]
\textbf{1. Launch Translational Demonstrators by 2027:}\\
UKRI, Horizon Europe, and national innovation agencies should establish dedicated calls for DRP-to-processing demonstrators. Each project should require a tripartite consortium spanning imaging science, orebody owner or recycler, and process scale-up capability. A practical target would be three to five pilot projects that move from characterization to pilot-plant decisions within 24--36 months.

\vspace{2mm}
\textbf{2. Define a ``Digital Ore Passport'' Standard by 2027:}\\
Regulators, geological surveys, and research infrastructures should publish a minimum data specification for publicly supported mining, recycling, and tailings projects. At a minimum, this should include multi-modal imaging metadata, mineralogical ground truth, uncertainty estimates, and machine-readable process descriptors. The goal should be adoption across all publicly funded pilot projects by 2028.

\vspace{2mm}
\textbf{3. Stand Up a Federated European Digital Ore Database by 2028:}\\
The European Commission, national geological surveys, and major imaging facilities should create a shared repository with open metadata, benchmark datasets, and application programming interfaces for model development. A reasonable first milestone would be 100 well-annotated benchmark datasets covering hard-rock ores, tailings, and battery-recycling feedstocks within the first two years.

\vspace{2mm}
\textbf{4. Build Workforce Capacity with Cross-Disciplinary Training Centres:}\\
The UK and Europe should fund doctoral and industrial training centres focused on the intersection of imaging, machine learning, mineral processing, and recycling. The point is not only to train students, but to create a talent pipeline that can move between beamlines, laboratories, software teams, and pilot plants. A useful benchmark would be two to three centres and at least 40 jointly supervised researchers by 2030.
\end{tcolorbox}

\section{Conclusion}
Leveraging the existing Digital Rock Physics community gives the UK and Europe a plausible route to differentiation in the race for secure and sustainable critical minerals. By transitioning this expertise from hydrocarbons to hard rocks and orchestrating a wide range of imaging modalities to characterize both ores and engineered porous materials, the region can improve how it explores, processes, and recycles mineral resources while strengthening supply-chain resilience for the energy transition.

\begin{thebibliography}{99}

\bibitem{drp_blunt_2013}
Blunt, M.J., Bijeljic, B., Dong, H., Gharbi, O., Iglauer, S., Mostaghimi, P., Paluszny, A., \& Pentland, C., ``Pore-scale imaging and modelling,'' \textit{Advances in Water Resources}, 51, 197--216, 2013. DOI: \url{https://doi.org/10.1016/j.advwatres.2012.03.003}.

\bibitem{lishchuk_predictive_2019}
Lishchuk, V., Lund, C., \& Ghorbani, Y., ``Evaluation and comparison of different machine-learning methods to integrate sparse process data into a spatial model in geometallurgy,'' \textit{Minerals Engineering}, 138, 144--153, 2019. DOI: \url{https://doi.org/10.1016/j.mineng.2019.01.032}.

\bibitem{ai_mineral_prospectivity_2011}
Zuo, R., \& Carranza, E.J.M., ``Support vector machine: A tool for mapping mineral prospectivity,'' \textit{Computers \& Geosciences}, 37(12), 1967--1975, 2011. DOI: \url{https://doi.org/10.1016/j.cageo.2010.09.014}.

\bibitem{norgate_comminution_2010}
Norgate, T., \& Haque, N., ``Energy and greenhouse gas impacts of mining and mineral processing operations,'' \textit{Journal of Cleaner Production}, 18(3), 266--274, 2010. DOI: \url{https://doi.org/10.1016/j.jclepro.2009.09.020}.

\bibitem{kyle_processing_2015}
Kyle, J.R., \& Ketcham, R.A., ``Application of high resolution X-ray computed tomography to mineral deposit origin, evaluation, and processing,'' \textit{Ore Geology Reviews}, 65, 821--839, 2015. DOI: \url{https://doi.org/10.1016/j.oregeorev.2014.09.034}.

\bibitem{mri_heap_leach_2015}
Fagan-Endres, M.A., Harrison, S.T.L., Johns, M.L., \& Sederman, A.J., ``Magnetic resonance imaging characterisation of the influence of flowrate on liquid distribution in drip irrigated heap leaching,'' \textit{Hydrometallurgy}, 157, 116--124, 2015. DOI: \url{https://doi.org/10.1016/j.hydromet.2015.10.003}.

\bibitem{mofs_lithium_2026}
Cao, X., Gao, H., \& Zeng, Y., ``Metal-organic frameworks for extraction of radionuclide/noble metals/lithium,'' in \textit{Metal Organic Frameworks for Energy and Environmental Applications}, 13--33, 2026. DOI: \url{https://doi.org/10.1016/B978-0-443-40377-4.00002-1}.

\bibitem{araya_tailings_2020}
Araya, N., Kraslawski, A., \& Cisternas, L.A., ``Towards mine tailings valorization: Recovery of critical materials from Chilean mine tailings,'' \textit{Journal of Cleaner Production}, 263, 121555, 2020. DOI: \url{https://doi.org/10.1016/j.jclepro.2020.121555}.

\bibitem{battery_blackmass_2021}
Vanderbruggen, A., Gugala, E., Blannin, R., Bachmann, K., Serna-Guerrero, R., \& Rudolph, M., ``Automated mineralogy as a novel approach for the compositional and textural characterization of spent lithium-ion batteries,'' \textit{Minerals Engineering}, 169, 106924, 2021. DOI: \url{https://doi.org/10.1016/j.mineng.2021.106924}.

\bibitem{buyse_correlative_2023}
Buyse, F., Dewaele, S., Boone, M.N., \& Cnudde, V., ``Combining Automated Mineralogy with X-ray Computed Tomography for Internal Characterization of Ore Samples at the Microscopic Scale,'' \textit{Natural Resources Research}, 32(2), 461--478, 2023. DOI: \url{https://doi.org/10.1007/s11053-023-10161-z}.

\bibitem{graczyk_dl_porosity_2020}
Graczyk, K.M., \& Matyka, M., ``Predicting porosity, permeability, and tortuosity of porous media from images by deep learning,'' \textit{Scientific Reports}, 10, 21459, 2020. DOI: \url{https://doi.org/10.1038/s41598-020-78415-x}.

\bibitem{karniadakis_piml_2021}
Karniadakis, G.E., Kevrekidis, I.G., Lu, L., Perdikaris, P., Wang, S., \& Yang, L., ``Physics-informed machine learning,'' \textit{Nature Reviews Physics}, 3, 422--440, 2021. DOI: \url{https://doi.org/10.1038/s42254-021-00314-5}.

\bibitem{raissi_pinns_2019}
Raissi, M., Perdikaris, P., \& Karniadakis, G.E., ``Physics-informed neural networks: A deep learning framework for solving forward and inverse problems involving nonlinear partial differential equations,'' \textit{Journal of Computational Physics}, 378, 686--707, 2019. DOI: \url{https://doi.org/10.1016/j.jcp.2018.10.045}.

\bibitem{ml_upscaling_drp_2024}
You, J., \& Lee, K.J., ``Upscaling reactive transport models from pore-scale to continuum-scale using deep learning method,'' \textit{Geoenergy Science and Engineering}, 242, 212850, 2024. DOI: \url{https://doi.org/10.1016/j.geoen.2024.212850}.

\bibitem{matter_carbfix_2009}
Matter, J.M., Broecker, W.S., Stute, M., Gislason, S.R., Oelkers, E.H., Stefansson, A., \textit{et al.}, ``Permanent Carbon Dioxide Storage into Basalt: The CarbFix Pilot Project, Iceland,'' \textit{Energy Procedia}, 1(1), 3641--3646, 2009. DOI: \url{https://doi.org/10.1016/j.egypro.2009.02.160}.

\bibitem{kelemen_peridotite_2020}
Kelemen, P.B., McQueen, N., Wilcox, J., Renforth, P., Dipple, G., \& Vankeuren, A.P., ``Engineered carbon mineralization in ultramafic rocks for CO2 removal from air: Review and new insights,'' \textit{Chemical Geology}, 550, 119628, 2020. DOI: \url{https://doi.org/10.1016/j.chemgeo.2020.119628}.

\bibitem{menke_hydrogen_2024}
Jangda, Z., Menke, H., Busch, A., Geiger, S., Bultreys, T., \& Singh, K., ``Subsurface hydrogen storage controlled by small-scale rock heterogeneities,'' \textit{International Journal of Hydrogen Energy}, 72, 467--482, 2024. DOI: \url{https://doi.org/10.1016/j.ijhydene.2024.02.233}.

\bibitem{bartels_fast_xray_2017}
Bartels, W.-B., Lin, Q., de Winter, D.A.M., Mahani, H., Berg, S., Cnudde, V., \& Ajo-Franklin, J.B., ``Fast X-Ray Micro-CT Study of the Impact of Brine Salinity on the Pore-Scale Fluid Distribution During Waterflooding,'' \textit{Petrophysics}, 58(1), 36--47, 2017.

\bibitem{farber_science_2025}
Farber, E.M., Seraphim, N.M., Tamakuwala, K., Stein, A., Rücker, M., \& Eisenberg, D., ``Porous materials: The next frontier in energy technologies,'' \textit{Science}, 387(6730), eadn9391, 2025. DOI: \url{https://doi.org/10.1126/science.adn9391}.

\bibitem{digitalrocks_portal_2023}
Prodanović, M., Esteva, M., McClure, J., Chang, B.C., Santos, M., Radhakrishnan, S., \textit{et al.}, ``Digital Rocks Portal (Digital Porous Media): Connecting data, simulation and community,'' \textit{E3S Web of Conferences}, 367, 01010, 2023. DOI: \url{https://doi.org/10.1051/e3sconf/202336701010}.

\bibitem{calvo_copper_2016}
Calvo, G., Mudd, G., Valero, A., \& Valero, A., ``Decreasing Ore Grades in Global Metallic Mining: A Theoretical Issue or a Global Reality?,'' \textit{Resources}, 5(4), 36, 2016. DOI: \url{https://doi.org/10.3390/resources5040036}.

\bibitem{iea_outlook_2025}
International Energy Agency (IEA), \textit{Global Critical Minerals Outlook 2025}, IEA, Paris, 2025. \url{https://www.iea.org/reports/global-critical-minerals-outlook-2025}.

\bibitem{eu_crma_2024}
European Union, ``Regulation (EU) 2024/1252 of the European Parliament and of the Council of 11 April 2024 establishing a framework for ensuring a secure and sustainable supply of critical raw materials,'' \textit{Official Journal of the European Union}, 2024. \url{https://eur-lex.europa.eu/eli/reg/2024/1252/oj/eng}.

\bibitem{uk_strategy_2022}
HM Government, \textit{Resilience for the Future: The UK's Critical Minerals Strategy}, London, 2022. \url{https://www.gov.uk/government/publications/uk-critical-mineral-strategy}.

\bibitem{doe_arpae}
Advanced Research Projects Agency-Energy (ARPA-E), \textit{ARPA-E FY 2023 Annual Report to Congress}, U.S. Department of Energy, August 2025. \url{https://arpa-e.energy.gov/sites/default/files/2025-09/ARPA-E%20FY%202023%20Annual%20Report.pdf}.

\bibitem{doe_mine_future_2025}
U.S. Department of Energy, ``Funding Notice: Mine of the Future -- Proving Ground Initiative,'' Hydrocarbons and Geothermal Energy Office, November 14, 2025. \url{https://www.energy.gov/hgeo/funding-notice-mine-future-proving-ground-initiative}.

\bibitem{netl_digitalrocks}
National Energy Technology Laboratory (NETL), \textit{Digital Rocks Portal}, U.S. Department of Energy. \url{https://digitalporousmedia.org/digital-rocks-portal-tombstone/}. Accessed March 24, 2026.

\bibitem{diamond_tomography_2026}
Diamond Light Source, ``Tomography,'' \textit{Imaging Techniques}, \url{https://www.diamond.ac.uk/Instruments/Techniques/Imaging/Tomography.html}. Accessed March 24, 2026.

\bibitem{esrf_bm05_2026}
European Synchrotron Radiation Facility (ESRF), ``BM05 - Industrial Imaging beamline,'' \url{https://www.esrf.fr/fr/home/UsersAndScience/Experiments/BM05.html}. Accessed March 24, 2026.

\bibitem{psi_tomcat_2025}
Paul Scherrer Institute (PSI), ``Beamline Information | BL: SLS/TOMCAT,'' \url{https://www.psi.ch/de/sls/tomcat/beamlines}. Accessed March 24, 2026.

\end{thebibliography}

\end{document}
